Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2015-10-13 paper.tex
Remove spectra noise todo item
Offer explanation on the low energy in the 6f_b frequency
Typo

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, a commonly used tool for
airfoil analysis, e.g. \cite{Castelli2011, Walker2014}, implemented as part of
the open source turbine design software QBlade \cite{Marten2013}. Simulations
were run for an angle of attack range of 0--40 degrees, in increments of 0.5
degrees. Solver parameters used a 100 panels, a fixed speed, zero Mach number,
\texttt{NCrit=9} (default $\mathrm{e}^n$ transition criteria parameter for an
average wind tunnel), and no forced boundary layer transition. Characteristics
for computed for the approximate average blade chord Reynolds numbers
encountered in the tow tank experiments.

@@

Spectra of the cross-stream velocity normalized by the free stream are plotted
in Figure~\ref{fig:wake-spectra} for regions on either side of the turbine. On
the $-y$ side of the turbine there is broadband turbulence produced by blade
stall, and on the $+y$ side there is a clear peak in the spectra caused by the
blade passage. We see that on both sides there is higher spectral energy at
lower Reynolds numbers. On the $+y$ side of the turbine we notice higher
spectral energy at the blade passage frequency's first harmonic, or $6
f_\mathrm{turbine}$.

\todo[inline]{Look at how spectra change when turbine rotational frequency
changes relative to inertial subrange.}

\todo[inline]{Make sure the spectra are not just shifting due to normalizing the
noise.}

>>>>

To help understand---and possibly predict---the $Re$-sensitivity on turbine
performance, a series of static foil coefficient datasets were computed with the
XFOIL viscous panel method code \cite{Drela1989}, a commonly used tool for
airfoil analysis, e.g. \cite{Castelli2011, Walker2014}, implemented as part of
the open source turbine design software QBlade \cite{Marten2013}. Simulations
were run for an angle of attack range of 0--40 degrees, in increments of 0.5
degrees. Solver parameters used a 100 panels, a fixed speed, zero Mach number,
\texttt{NCrit=9} (default $\mathrm{e}^n$ transition criteria parameter for an
average wind tunnel), and no forced boundary layer transition. Characteristics
were computed for the approximate average blade chord Reynolds numbers
encountered in the tow tank experiments.

@@

Spectra of the cross-stream velocity normalized by the free stream are plotted
in Figure~\ref{fig:wake-spectra} for regions on either side of the turbine. On
the $-y$ side of the turbine there is broadband turbulence produced by blade
stall, and on the $+y$ side there is a clear peak in the spectra caused by the
blade passage. We see that on both sides there is higher spectral energy at
lower Reynolds numbers. On the $+y$ side of the turbine we notice higher
spectral energy at the blade passage frequency's first harmonic, or $6
f_\mathrm{turbine}$. This is likely due to the blade's shed vorticity being less
stable at higher $Re$.
